%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%

%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-orange}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
% \photo[circle,edge,right]{./profile.png}
\name{Tom}{Leverstone}
\position{Senior Software Engineer}
% \address{London}

\mobile{07397965017}
\email{tleverstone@gmail.com}
\homepage{leverstone.me}
\github{nagasaki45}
\linkedin{tleverstone}
% \gitlab{your-gitlab}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{medium-id}
% \googlescholar{googlescholar-id}{name-to-display}

% \quote{``A witty and insightful quote" - Someone}

%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal information
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[C]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Tom Leverstone~~~·~~~CV}
  {\thepage}

%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Skills}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvskills}
%---------------------------------------------------------
  \cvskill
    {Soft Skills} % Category
    {Team player, Self learner, Strive for quality, Attention to details, Teaching and mentoring} % Skills

%---------------------------------------------------------
  \cvskill
    {Backend} % Category
    {Python with Django or FastAPI} % Skills

%---------------------------------------------------------
  \cvskill
    {AI} % Category
    {Retrieval-Augmented Generation with LangChain} % Skills

%---------------------------------------------------------
  \cvskill
    {Frontend} % Category
    {React.js, Next.js, and TypeScript} % Skills

%---------------------------------------------------------
  \cvskill
    {Tools} % Category
    {Linux, Git, and Docker} % Skills

%---------------------------------------------------------
\end{cvskills}

%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {Mintel} % Organization
    {London} % Location
    {Since 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designing and leading the development of a backend service for an AI-powered question-and-answer system.}
        \item {This Retrieval-Augmented Generation service consolidated logic that previously lived in a frontend application and a thread-based Django server, to an asynchronous FastAPI server, significantly improving the system's load-handling capacity, decoupling the frontend from the backend, and facilitating the implementation of new features.}
        \item {Addressing critical bottlenecks in data preparation and indexing, reducing processing time for ingesting our entire dataset from three to one hour, while improving the process robustness.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Mintel} % Organization
    {London} % Location
    {2021 - 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Working full-stack on a web app that allows clients to search and read content written by Mintel's market research analysts. Taking active part in all team activities of an established Scrum team.}
        \item {Leading the development of a Single Page App for long-form content consumption written in React, including backend API development in Django.}
        \item {Advocating for high code quality by improving the team documentation, test suites, and alerting system (Sentry).}
        \item {Collaborating autonomously with adjacent teams, including contributing code to accelerate the development of features and bug fixes for the teams' dependencies.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Full-stack Developer} % Job title
    {Queen Mary University of London} % Organization
    {London} % Location
    {2020 - 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Migrating the wordpress website of the Media and Arts Technology centre to Gatsby.js, hosted on GitHub pages, with continuous delivery by travis-ci.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Python Back-end Developer} % Job title
    {XtremIO} % Organization
    {Israel} % Location
    {2014 - 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Working on the management server of an enterprise storage array.}
        \item {Developing automated maintenance procedures such as system upgrades, hardware replacements, restores, migrations, etc.}
        \item {Designing and implementing high-level and interactive protocols for client-server communication.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Python and Django tutor} % Job title
    {Freelance and with Udi Oron} % Organization
    {Israel} % Location
    {2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Teaching programmers in tech companies and privately.}
        \item {Developing teaching materials as well as teaching and assisting in class.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Full-stack Developer} % Job title
    {Shachar Web Solutions} % Organization
    {Israel} % Location
    {2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developing an enterprise resource planning system with Django and jQuery.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Math tutor} % Job title
    {Freelance and at HighQ retake college} % Organization
    {Israel} % Location
    {2009 - 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Teaching mathematics to 7th-12th grade students including preparation for matriculation exams (Israeli equivalent to A level) both privately and at a retake college.}
        \item {Teaching BSc students Linear Algebra, Calculus, Discrete Mathematics, Probability, Statistics and more at undergraduate level.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}

%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {PhD in Computer Science} % Degree
    {Queen Mary University of London} % Institution
    {London} % Location
    {2016 - 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {\textbf{Thesis title:} Head movement in conversation}
        \item {\textbf{Supervisors:} Prof. Patrick Healey and Dr. Julian Hough}
        \item {This PhD explores the function and form of head movement and specifically head nods in free conversation.}
        \item {It utilizes virtual reality and motion capture data analysis to explore listeners non-verbal cues in multiparty social interactions.}
        \item {Overall, this thesis questions the coherence of our intuitive notion of a head nod and the adequacy of current approaches to describe the movements involved.}
        \item {It shows how some of the common theories that describe head movement and nods fail to explain most head movement in free conversation.}
        \item {In addition, it highlights subtleties in head movement and nods that are often overlooked.}
        \item {\textbf{Activities:}}
        \item {Designing and running software skills workshops: Intro to Code with Python/Processing, Data Analysis with Python and Pandas, and Version Control with Git.}
        \item {Teaching assistance for ``Interactive Digital Multimedia Techniques'', ``Parallel Computing'', and ``Arts Application Programming'' modules.}
        \item {Organising the Virtual Reality Special Interest Group.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {MA in Music Technology} % Degree
    {Bar-Ilan University} % Institution
    {Israel} % Location
    {2011 - 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {\textit{Exceptional distinction (97\%)}}
        \item {\textbf{Thesis title:} An Audio-Only Augmented Reality System for Social Interaction}
        \item {\textbf{Supervisors:} Prof. Eitan Avitsur and Dr. Nori Jacoby.}
        \item {This thesis examines how an interactive environment might facilitate social interaction by developing and evaluating a mobile app for joint music consumption by a group of users in the same place and time.}
        \item {The app measure relative distances from a set of beacons via Bluetooth, and generates an immersive personalised musical environment that depends on the location of its participants.}
        \item {Two experiments tested the system in the context of a silent disco party, using the system's relative position signals as well as video tracking to evaluate the experience of users.}
        \item {The results showed that the system promoted openness and increased the social interaction between users.}
        \item {\textbf{Activities:}}
        \item {Organising the weekly seminars of the Music Technology programme.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {BSc in Mathematics and Music} % Degree
    {Haifa University} % Institution
    {Israel} % Location
    {2006 - 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {\textbf{Activities:}}
        \item {Participating in the excellence programme of the department of mathematics.}
        \item {Taking part in establishing and maintaining the computer lab of the music department.}
        \item {Working as a recording and mixing engineer in the music department recording studio.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}

%-------------------------------------------------------------------------------
\end{document}
